First paper - Draft

### 2017-06-19 paper/paper.Rnw
Implemented graphs for % increase/decrease + sample size tables

@@

% How to output data frames are latex tables?
<<perc_increase_tables, cache = TRUE>>=

# Show the rates at which is increasing/decreasing
perc_increase_fun <- function(df) {

@@

      .x %>%
        transmute(type_test,
                  country,
                  perc_diff = round(((!!last_year) - (!!first_year)) / (!!first_year) * 100, 1),
                  sd_year = year_sd,
                  diff_lower = perc_diff - 1 * year_sd,
                  diff_upper = perc_diff + 1 * year_sd,
                  years_available = years_available)
    })
  data_ready
}

@@

>>>>

\section{Descriptives}

@@

% How to output data frames are latex tables?
<<perc_increase_tables, cache = TRUE>>=
df <- split(
  group_by(complete_data_topmid, type_test) %>% select(wave, country, type_test, difference), complete_data_topmid$country)
.x <- df$`United States`
# Show the rates at which is increasing/decreasing
perc_increase_fun <- function(df) {

@@

      .x %>%
        map_if(is_double, round, 3) %>%
        as_tibble() %>%
        transmute(type_test,
                  country,
                  perc_diff = round(((!!last_year) - (!!first_year)) * 100, 1),
                  sd_year = year_sd,
                  diff_lower = perc_diff - 1 * year_sd,
                  diff_upper = perc_diff + 1 * year_sd,
                  years_available = years_available)
    })
  data_ready
}

@@

<<graphing_perc_increase, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
perc_graph <- function(df) {
  df %>%
  enframe(name = "country") %>%
  unnest(value) %>%
  filter(country %in% countries) %>%
  select(-country1, -years_available) %>%
  mutate(diff_95_lower = perc_diff - 2*sd_year,
         diff_95_upper = perc_diff + 2*sd_year) %>%
  setNames(c("Country", "Type of test", "Average % difference", "Average SD",
             "Lower 50% bound", "Upper 50% bound", "Lower 95% bound", "Upper 95% bound")) %>%
  filter(`Type of test` == "math") %>%
  arrange(`Average % difference`) %>%
  mutate(Country = ordered(forcats::as_factor(Country)),
         Country_num = as.numeric(Country)) %>%
  ggplot(aes(Country, `Average % difference`)) +
  geom_point() +
  geom_ribbon(aes(x = Country_num, ymin = `Lower 95% bound`, ymax = `Upper 95% bound`), alpha = 0.5) +
  geom_ribbon(aes(x = Country_num, ymin = `Lower 50% bound`, ymax = `Upper 50% bound`), alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "longdash") +
  scale_y_continuous(breaks = seq(-160, 160, 40)) +
  coord_cartesian(ylim = c(-160, 160)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
}

m1 <- perc_graph(top_bottom_perc)
m2 <- perc_graph(top_mid_perc)
m3 <- perc_graph(mid_bottom_perc)

gridExtra::grid.arrange(m1, m2, m3, nrow = 1)
@

<<table_sample>>=
sample_tables_topbottom %>%
  filter(name %in% c(2000, 2015)) %>%
  transmute(name, country, escs_dummy, N = paste0(n, " (", perc, ")")) %>%
  spread(escs_dummy, N) %>%
  rename(Year = name,
         Country = country,
         `10th SES` = `0`,
         `90th SES` = `1`) %>%
  select(Country, Year, everything()) %>%
  arrange(Country, Year) %>%
  xtable::xtable()
@
